Cell Decompositions for Rank Two Quiver Grassmannians

### 2019-06-17 Grassmannian_cells.tex
Typo fixes

  To see the final claim, there are three cases to consider.
  The case $|J|=n-1$ is immediate from the construction above.
  When $|J|<n-2$, we may find subsets $I,I'\subsetneq\{1,\ldots,n\}$ with $J\subsetneq I,I'$, $I\setminus J=\{j\}$, $I'\setminus J=\{j'\}$, and $j\ne j'$.
  This gives rise to the following commutative diagram:
  \[\xymatrix{& & 0\ar[d]& 0\ar[d]&\\
    & & \tilde P_{m,j'}\ar[d]\ar@{=}[r]& \tilde P_{m,j'}\ar[d]&\\
    0\ar[r]&\tilde P_{m,j} \ar[r]\ar@{=}[d] & \tilde P_{m+1}^J\ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & \tilde P_{m+1}^I\ar[r]\ar[d]& 0\\
    0\ar[r] &\tilde P_{m,j}\ar[r] &  \tilde P_{m+1}^{I'}\ar[r]\ar[d] & \tilde P_{m+1}^{I\cup I'}\ar[r]\ar[d] & 0\\
  & & 0& 0&}\]
  Let $A:=\AA^d\times B\times C$ be an affine cell for $\Gr_\tbfe(\tilde P_{m+1}^J)$ constructed as above using this middle horizontal sequence, say with $B$ an affine cell of $\Gr_\tbff(\tilde P_{m,j})$ and $C$ an affine cell of $\Gr_\tbfg(\tilde P_{m+1}^I)$.
  Thus, for $\tilde E\in A$, we have $\tilde E\cap P_{m,j}\in B$ and $\tilde\pi_{m+1}^{I,J}(\tilde E)\in C$.
  Similarly, the affine cell $C$ can be written as $\AA^{d'}\times B'\times D$ with $B'$ an affine cell of $\Gr_{\tbff'}(\tilde P_{m,j'})$ and $D$ an affine cell of $\Gr_\tbfh(\tilde P_{m+1}^{I\cup I'})$ so that elements $\tilde G\in C$ satisfy $\tilde G\cap \tilde P_{m,j'}\in B'$ and $\tilde\pi_{m+1}^{I\cup I',I}(\tilde G)\in D$.
  In particular, this implies $\tilde E\cap \tilde P_{m,j'}\in B'$ and $\tilde\pi_{m+1}^{I\cup I',J}(\tilde E)\in D$ for any $\tilde E\in A$.
  Then for $\tilde E\in A$, writing $\tilde G'=\tilde\pi_{m+1}^{I',J}(\tilde E)$, we see $\tilde\pi_{m+1}^{I',J}(\tilde G')\in D$ and $\tilde G'\cap \tilde P_{m,j}\in B$.
  Thus $\tilde\pi_{m+1}^{I',J}(\tilde E)$ lies in an affine cell $C':=\AA^{d''}\times B\times D$ for $\Gr_{\tbfg'}(\tilde P_{m+1}^{I'})$.
  The induced map $A\to B'\times C'$, $\tilde E\mapsto \big(\tilde E\cap \tilde P_{m,j'},\tilde\pi_{m+1}^{I',J}(\tilde E)\big)$, is surjective by a routine chase through the diagram above.
  For any $\tilde E\in Gr_\tbfe(\tilde P_{m+1}^J)$ with $\tilde E\cap \tilde P_{m,j'}\in B'$ and $\tilde\pi_{m+1}^{I',J}(\tilde E)\in C'$, the following hold:
  \begin{itemize}
    \item $\tilde E\cap \tilde P_{m,j}=\tilde\pi_{m+1}^{I',J}(\tilde E)\cap \tilde P_{m,j}\in B$;
    \item writing $\tilde G=\tilde\pi_{m+1}^{I,J}(\tilde E)$, we have $\tilde G\cap \tilde P_{m,j'}=\tilde E\cap \tilde P_{m,j'}\in B'$ and $\tilde\pi_{m+1}^{I\cup I',I}(\tilde G)\in D$ so that $\tilde\pi_{m+1}^{I,J}(\tilde E)\in C$.
  \end{itemize}
  It follows that $\tilde E\in A$ and thus $A$ identifies with the affine cell for $\Gr_\tbfe(\tilde P_{m+1}^J)$ constructed from the affine cells $B'$ and $C'$ using the middle vertical sequence in the diagram above.

>>>>

  To see the final claim, there are three cases to consider.
  The case $|J|=n-1$ is immediate from the construction above.
  When $|J|<n-2$, we may find subsets $I,I'\subsetneq\{1,\ldots,n\}$ containing $J$ so that $I\setminus J=\{j\}$, $I'\setminus J=\{j'\}$, and $j\ne j'$.
  This gives rise to the following commutative diagram:
  \[\xymatrix{& & 0\ar[d]& 0\ar[d]&\\
    & & \tilde P_{m,j'}\ar[d]\ar@{=}[r]& \tilde P_{m,j'}\ar[d]&\\
    0\ar[r]&\tilde P_{m,j} \ar[r]\ar@{=}[d] & \tilde P_{m+1}^J\ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & \tilde P_{m+1}^I\ar[r]\ar[d]& 0\\
    0\ar[r] &\tilde P_{m,j}\ar[r] &  \tilde P_{m+1}^{I'}\ar[r]\ar[d] & \tilde P_{m+1}^{I\cup I'}\ar[r]\ar[d] & 0\\
  & & 0& 0&}\]
  Let $A:=\AA^d\times B\times C$ be an affine cell for $\Gr_\tbfe(\tilde P_{m+1}^J)$ constructed as above using this middle horizontal sequence, say with $B$ an affine cell of $\Gr_\tbff(\tilde P_{m,j})$ and $C$ an affine cell of $\Gr_\tbfg(\tilde P_{m+1}^I)$.
  Thus, for $\tilde E\in A$, we have $\tilde E\cap P_{m,j}\in B$ and $\tilde\pi_{m+1}^{I,J}(\tilde E)\in C$.
  Similarly, the affine cell $C$ can be written as $\AA^{d'}\times B'\times D$ with $B'$ an affine cell of $\Gr_{\tbff'}(\tilde P_{m,j'})$ and $D$ an affine cell of $\Gr_\tbfh(\tilde P_{m+1}^{I\cup I'})$ so that elements $\tilde G\in C$ satisfy $\tilde G\cap \tilde P_{m,j'}\in B'$ and $\tilde\pi_{m+1}^{I\cup I',I}(\tilde G)\in D$.
  In particular, this implies $\tilde E\cap \tilde P_{m,j'}\in B'$ and $\tilde\pi_{m+1}^{I\cup I',J}(\tilde E)\in D$ for any $\tilde E\in A$.
  Then for $\tilde E\in A$, writing $\tilde G'=\tilde\pi_{m+1}^{I',J}(\tilde E)$, we see $\tilde G'\cap \tilde P_{m,j}\in B$ and $\tilde\pi_{m+1}^{I\cup I',I'}(\tilde G')\in D$.
  Thus $\tilde\pi_{m+1}^{I',J}(\tilde E)$ lies in an affine cell $C':=\AA^{d''}\times B\times D$ for $\Gr_{\tbfg'}(\tilde P_{m+1}^{I'})$.
  The induced map $A\to B'\times C'$, $\tilde E\mapsto \big(\tilde E\cap \tilde P_{m,j'},\tilde\pi_{m+1}^{I',J}(\tilde E)\big)$, is surjective by a routine chase through the diagram above.
  For any $\tilde E\in Gr_\tbfe(\tilde P_{m+1}^J)$ with $\tilde E\cap \tilde P_{m,j'}\in B'$ and $\tilde\pi_{m+1}^{I',J}(\tilde E)\in C'$, the following hold:
  \begin{itemize}
    \item $\tilde E\cap \tilde P_{m,j}=\tilde\pi_{m+1}^{I',J}(\tilde E)\cap \tilde P_{m,j}\in B$;
    \item writing $\tilde G=\tilde\pi_{m+1}^{I,J}(\tilde E)$, we have $\tilde G\cap \tilde P_{m,j'}=\tilde E\cap \tilde P_{m,j'}\in B'$ and $\tilde\pi_{m+1}^{I\cup I',I}(\tilde G)\in D$ so that $\tilde\pi_{m+1}^{I,J}(\tilde E)\in C$.
  \end{itemize}
  It follows that $\tilde E\in A$ and thus $A$ identifies with the affine cell for $\Gr_\tbfe(\tilde P_{m+1}^J)$ constructed from the affine cells $B'$ and $C'$ using the middle vertical sequence in the diagram above.
